QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-01 Revision/Paper_Rev.tex
Rev_V3.1

\newpage.\newpage

\subsection{QoE Function}
\textcolor{brown}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. When the MD is operating in performance mode, the MD's preference is to minimize task delays. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption.
Based on the system model, we first formulate the calculation of task delay, energy consumption, and associated cost, and then represent the QoE function accordingly.}

@@

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +$
\begin{alignat}{1}
	\;\;\;\; x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} y_{i,j}(t) \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ when task $z_i(t)$ is dropped. Correspondingly, we denote the energy consumption of task $z_i(t)$ when taking action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$ as $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, which is: \vspace{1.7mm}

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
\hspace{1.8cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}

Given the delay and energy consumtion of task $z_i(t)$, we also define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$. \vspace{1.7mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. When the MD is operating in performance mode, the delay contributes more to the cost than energy consumption. Otherwise, when the MD switches to ultra power-saving mode, the energy consumption contributes more to the cost than delay due to main attention on reducing power consumption.

Finally, we define $\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ as the QoE associated with task $z_i(t)$ given the selected action $\boldsymbol{a}_i(t)$ and the observed state $\boldsymbol{s}_i(t)$. The QoE function is defined as follows:\vspace{1.7mm}

$\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
 \hspace*{8mm}
	\begin{cases} 
		\mathcal{R} - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) & \hspace*{-2mm} \text{if task $z_i(t)$ is processed,} \\
		- \hspace*{0.8mm} \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) &	\hspace*{-2mm} \text{if task $z_i(t)$ is dropped,}
	\end{cases}
	\label{26}  
\end{alignat}
where $\mathcal{R} > 0$ represents a constant reward for task completion. If $z_i(t) = 0$, then $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t)) = 0$. Throughout the rest of this paper, we adopt the shortened notation $\boldsymbol{q}_i(t)$ to represent $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$.
%When $\phi_i(t)$ is closer to 1, the cost function prioritizes reducing delay and drop, which could be advantageous in situations where tasks need to be completed quickly, and responsiveness is crucial. Conversely, when $\phi_i(t)$ is closer to 0, the cost function prioritizes reducing energy consumption, which is beneficial when the MD's battery level is low, and conserving power is necessary to prolong operation.

\newpage.\newpage

>>>>

\subsection{QoE Function}
%\textcolor{brown}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. When the MD is operating in performance mode, the MD's preference is to minimize task delays. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption. Based on the system model, we first formulate the calculation of task delay, energy consumption, and associated cost, and then represent the QoE function accordingly.}

\textcolor{blue}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. 
Based on the system model, we first formulate the calculation of task delay and energy consumption and then represent the associated cost and QoE function accordingly.}

@@

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)$
\begin{alignat}{1}
	\;\;\;\,\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
\textcolor{blue}{where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ if task $z_i(t)$ is dropped. Accordingly, the energy consumption for task $z_i(t)$ under action $\boldsymbol{a}_i(t)$ in observed state $\boldsymbol{s}_i(t)$ is denoted as $\mathcal{E}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$, given by:}\vspace{2mm}

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
\hspace{0.9cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)}  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}

\textcolor{blue}{To define associated cost, we use a weighted sum between task delay $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ and energy consumption $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, where the weights adjust dynamically depending on the MD's energy levels to reflect the MD's preference for each factor.
Given the delay and energy consumtion of task $z_i(t)$, we define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$.} \vspace{2mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
\,\,\,\,\,\,\,\,\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. 
\textcolor{blue}{When the MD is operating in performance mode, the MD's preference is to minimize task delays, thus the delay contributes more to the cost than energy consumption. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption and the energy consumption contributes more to the cost than delay.}

\textcolor{blue}{Finally, we define an adaptive trade-off between task completion and cost reduction as the QoE associated with task $z_i(t)$. The QoE is affected by the increase in the number of completed tasks given by the task's complexity and reducing weighted cost. Given the selected action $\boldsymbol{a}_i(t)$ and the observed state $\boldsymbol{s}_i(t)$, we define The QoE function as follows,
\begin{alignat}{1}
\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = 	\mathcal{R}\, \lambda_i(t) \rho_i(t) - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))
\end{alignat}}
%\begin{alignat}{1}
% \hspace*{1mm}
%	\begin{cases} 
%		\mathcal{R}( \lambda_i(t) \rho_i(t)) - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) & \hspace*{-2mm} \text{if task $z_i(t)$ is processed,} \\
%		- \hspace*{0.8mm} \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) &	\hspace*{-2mm} \text{if task $z_i(t)$ is dropped,}
%	\end{cases}
%	\label{26}  
%\end{alignat}
where $\mathcal{R} > 0$ represents a constant reward for task completion. If $z_i(t) = 0$, then $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t)) = 0$. Throughout the rest of this paper, we adopt the shortened notation $\boldsymbol{q}_i(t)$ to represent $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$.
%When $\phi_i(t)$ is closer to 1, the cost function prioritizes reducing delay and drop, which could be advantageous in situations where tasks need to be completed quickly, and responsiveness is crucial. Conversely, when $\phi_i(t)$ is closer to 0, the cost function prioritizes reducing energy consumption, which is beneficial when the MD's battery level is low, and conserving power is necessary to prolong operation.
